---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Prerequisites

This assessment makes use of the [data.table](https://cran.r-project.org/web/packages/data.table/index.html) and [dplyr](https://cran.r-project.org/web/packages/dplyr/index.html) and [ggplot2](https://cran.r-project.org/web/packages/ggplot2/index.html) packages. Ensure they are installed (via `install.packages(c("data.table", "dplyr", "ggplot2"))`) before running any of the code here. data.table is probably overkill for the small data set we're looking at here, but it's invaluable for large data sets and I like to have a consistent set of tools to work with.

```{r}
library(data.table)
library(dplyr)
library(ggplot2)
```

We also assume that the data has already been unzipped and is available in the working directory as `activity.csv`.

## Loading and preprocessing the data

Load in the data; we perform two bits of preprocessing along the way:

1. Changing the `date` column into an actual date as we go
2. Changing the `interval` column into a simple number of minutes since midnight, rather than the original HHMM format. (`%/%` is the integer division operator and `%%` is the modulus operator)

```{r}
steps <- fread("activity.csv") %>%
  mutate(date = as.POSIXct(date)) %>%
  mutate(interval = 60 * (interval %/% 100) + interval %% 60)
```

## What is mean total number of steps taken per day?

Group the data by day and sum the number of steps:

```{r}
stepsByDay <- steps %>% group_by(date) %>% summarise(steps = sum(steps))
qplot(stepsByDay$steps, geom="histogram", xlab="Steps", ylab="Count")
```

And calculate the mean and median, ignoring missing values:

```{r}
mean(stepsByDay$steps, na.rm = TRUE)
median(stepsByDay$steps, na.rm = TRUE)
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
